mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2022-12-12 Draft3.Rmd
errors
small changes

The present R package defines a set of rules for an _automatic_ translation of
R expressions to mathematical output in RMarkdown documents [@Xie2020] and
ShinyApp webpages [@Chang2022]. The translation is done by an embedded Prolog
interpreter that maps nested expressions recursively to MathML and
LaTeX/MathJax, respectively. User-defined hooks enable to extend the set of
rules, for example, to represent specific R elements by custom mathematical
signs.

*todo*: mention that the _same_ R expression is used for mathematical
calculations and printing.

@@

@@

>>>>

The present R package defines a set of rules for an _automatic_ translation of
R expressions to mathematical output in RMarkdown documents [@Xie2020] and
ShinyApp webpages [@Chang2022]. The translation is done by an embedded Prolog
interpreter that maps nested expressions recursively to MathML and
LaTeX/MathJax, respectively. User-defined hooks enable to extend the set of
rules, for example, to represent specific R elements by custom mathematical
signs. Moreover, in addition to graphical rendering, the same R expression provides its calculation or evaluation. This feature of the package saves the user's time and allows faster detection of errors.

@@

```{r omit, echo=FALSE}
op <- list(left=quote(omit_left(a + b)), right=quote(omit_right(a + b)), list=quote(omit(c)))
m <- lapply(op, FUN=mathjax, flags=list(cat=FALSE))

t <- cbind(Operator=op, Output=m)
knitr::kable(t, caption="Omit", row.names=FALSE, escape=FALSE)
```

@@

```{r add, echo=FALSE}
op <- list(left=quote(add_left(a + b)), right=quote(add_right(a + b)), list=quote(add(c)))
m <- lapply(op, FUN=mathjax, flags=list(cat=FALSE))

t <- cbind(Operator=op, Output=m)
knitr::kable(t, caption="Add", row.names=FALSE, escape=FALSE)
```
